---
title: "`r params$name`"
author: "mastim"
date: "`r Sys.Date()`"

output: 
  html_document:
   css: ./table_style1.css
params: 
  fname: "report.ya.dif.csv"
  type: "dif"
  date1_start: ""
  date1_end: ""
  date2_start: ""
  date2_end: ""
  name: "report"
  prog_name: ""
  sourceMedium: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
date1_start <- params$date1_start#"2017-11-01"
date1_end <- params$date1_end#"2017-11-07"

date2_start <- params$date2_start#"2017-11-08"
date2_end <- params$date2_end#"2017-11-14"

fname <- params$fname#"report.ya.dif.csv"
#fname <- "report.ya.1.csv"

type <- params$type#"dif"
#type <- "plane"

period_text<-""

if (type == "plane"){
  period_text<-paste("period: ", date1_start, " - ", date1_end, sep="")
}else{
  period_text<-paste("period 1: ", date1_start, " - ", date1_end, "<p>", 
                     "period 2: ", date2_start, " - ", date2_end, sep="")
}
```

## Report


`r period_text`

### project: *`r params$prog_name`*

#### source / medium: *`r params$sourceMedium`*




```{r table_dif, echo=FALSE, cache=FALSE, warning=FALSE, comment=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(xtable)

report <- read.csv(fname)
#rename columns
#campaign_id	CampaignName	keyword	Cost	sessions	Impressions	Clicks	CPC	AvgClickPosition	AvgImpressionPosition	CTR	allGoalsCompletions	transactionRevenue	CPA	ROI
keywords<-report$keyword



colnames(report)<-c("campaign_id",	"Название кампании",	"Ключевые слова",	"Расход",	"Сессии",	"Показы",	"Клики",	"CPC",	"Ср. позиция клика",	"Ср. позиция показа",	"CTR",	"Достижения целей",	"Доход",	"CPA",	"ROI")

if(type == "dif"){
  print(xtable(report), type = "html", include.rownames = F, html.table.attributes='id="difTable" class="TFtable"')
} else {
  print(xtable(report), type = "html", include.rownames = F, html.table.attributes='id="planeTable" class="TFtable"')
}


```
<script type"text/javascript">
var t =$('.TFtable'); //jquery Table Object
var firstTR = $('tr:first',t); //geting firstTR
$('<thead class="fixedHeader"></thead>')
  .prependTo(t)
  .append(firstTR.clone());

firstTR.remove();//removing First TR


</script>

<script type="text/javascript">
var table = document.getElementById('difTable');
var tbody = table.getElementsByTagName('tbody')[0];
var rows = tbody.getElementsByTagName('tr');


for (var i=0, len=rows.length; i<len; i++){
    var cells = rows[i].getElementsByTagName('td');
    if(cells[2].innerText=="все"){
      rows[i].className = "summary-row";
    }
    for (var j=3, len2=cells.length; j<len2; j++){
      var cell_value = parseFloat(cells[j].innerHTML,10);
      if (cell_value < 0){
          if (cell_value > -20){
            cells[j].style.backgroundColor = '#ffcccc';
          }
          else if (cell_value > -50){
            cells[j].style.backgroundColor = '#ff6666';
          }
          else {
            cells[j].style.backgroundColor = '#ff0000';
          }
      }
      else if (cell_value > 0){
          if (cell_value < 20){
            cells[j].style.backgroundColor = '#ebfaeb';
          }
          else if (cell_value < 50){
            cells[j].style.backgroundColor = '#99e699';
          }
          else {
            cells[j].style.backgroundColor = '#33cc33';
          }
      }
    }
}


</script>
```{r wordcloud, echo=FALSE, cache=FALSE, warning=FALSE, comment=FALSE, warning=FALSE, message=FALSE, results='asis'}
library(tm)
keyword_edt<-Corpus(VectorSource(keywords),
       readerControl = list(reader = readPlain,
                            load = T))

keyword_edt <- tm_map(keyword_edt, stripWhitespace)
keyword_edt <- tm_map(keyword_edt, tolower)
keyword_edt <- tm_map(keyword_edt, removeNumbers)
keyword_edt <- tm_map(keyword_edt, removePunctuation)
keyword_edt <- tm_map(keyword_edt, removeWords, stopwords("russian"))
keyword_edt <- tm_map(keyword_edt, iconv, 'UTF-8', 'cp1251')


library(wordcloud)
wordcloud(keyword_edt, random.order=F, max.words=1000, 
          colors=brewer.pal(6,"Set1"))

```
